Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex
Moved 5.0 lemmas to the appendix and wrote sketch of cor 1 proof.

@@

We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. \jessiet{Going to suggest proof to appendix.}
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
  Now consider $v \in F - p$.
  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
  Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
%  
%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}

The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.\jessiet{Going to suggest entire lemma to appendix.}
\newcommand{\simplexp}{\Delta_{\Y'}}
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

We can now understand the subspace of feasible directions as a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
The following statement from~\citet{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.

\begin{corollary}[\citep{ramaswamy2016convex}]\label{cor:fsd-bound}
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
\end{corollary}
\begin{proof}
	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$, and consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
	Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.

	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
%	First, for intuition, consider $p \in \relint{\simplex}$. 
%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
%
%	
%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
%	
%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
%	\begin{align*}
%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
%	\end{align*}
%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
%
%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
\subsection{Example: high-confidence classification}\label{subsec:examples-finite}
There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
For example, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
For this example, we choose $p$ to be the uniform distribution.
In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
%% Bo: resolved on Jun 1, afternoon
%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}

@@

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
In continuous estimation problems, often one does not start with a target loss per se, but instead with a conditional statistic of the data one wishes to estimate, such as the conditional mean, variance, or entropy.
In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
In particular, following an argument from~\citet{frongillo2018elicitation}, below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses; our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
\raft{FYI to Jessie: what you had was all reasonable/true, but was a dispersed.  Which is understandable---just explaining the motivation for the edits.}

@@

\section{Omitted Proofs}\label{app:omitted-proofs}
\begin{proposition}\label{prop:elic-cplx-lb-ccdim}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
\end{proof}

>>>>

\usepackage{thmtools, thm-restate}
%\declaretheorem{corollary}

@@

We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$.

We can now understand the subspace of feasible directions as a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
The following statement from~\citet{ramaswamy2016convex} provides an upper bound on the convex calibration dimension of a given discrete loss, and now follows as a Corollary of our Theorem~\ref{thm:cvx-flats} and Lemma~\ref{lem:feas-sub-is-a-flat}.
Even with the proofs of these results, our proof of Corollary~\ref{cor:fsd-bound} is still shorter and (in our opinion) simpler than the original.
Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.

\begin{restatable}[\citep{ramaswamy2016convex}]{corollary}{hariresult}\label{cor:fsd-bound}
	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
	\begin{equation}
	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
\end{restatable}
\begin{proof}[Proof sketch]
	First, consider some $p \in \relint{\simplex}$ for intuition.
	Observe that $\Sc_{\gamma_r}(p) + p$ is a flat containing $p$ in $\affhull(\simplex)$, and moreover that  $\Sc_{\gamma_r}(p) + p \subseteq \gamma_r$.
	As Theorem~\ref{thm:cvx-flats} makes a statement about the existence of a flat $F'$ of codimension at most $d$, we know that $d \geq \codim(F') \geq \codim(\Sc_{\gamma_r}(p)) = n- \dim(\Sc_{\gamma_r}(p)) - 1$.
	Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, thus completing the proof for $p \in \relint{\simplex}$.

	When $p \not \in \relint{\simplex}$, we can loosely ``project down'' to the subsimplex on the support of $p$ and modify $L$ and $\ell$ so that the feasible subspace dimension on this modified space is the same relative to the subsimplex.
	Any flat containing $p$ in the original simplex can only have smaller codimension relative to $\reals^{\supp(p)}$.
	We can now apply Theorem~\ref{thm:cvx-flats} on the modified space; the dimension $\dim(\Sc_{\gamma_r}(p)) = \|p\|_0 - \codim(\Sc_{\gamma_r}(p)) - 1$ yields the bound.
\end{proof}

\subsection{Example: high-confidence classification}\label{subsec:examples-finite}
There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
For example, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and abstains from predicting ($\bot$) otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \mathbbm{1}\{r \not \in \{y, \bot\}\} + (1/2)\mathbbm{1}\{r = \bot\}$. 
We can consider two different distributions; in the first, our bound yields a strong gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
For this example, we choose $p$ to be the uniform distribution.
In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
%% Bo: resolved on Jun 1, afternoon
%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}

@@

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
In continuous estimation problems, often one does not start with a target loss per se, but instead with a conditional statistic of the data one wishes to estimate, such as the conditional mean, variance, or entropy.
In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
In particular, following an argument from~\citet{frongillo2018elicitation}, below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses; our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
\raft{FYI to Jessie: what you had was all reasonable/true, but was a dispersed.  Which is understandable---just explaining the motivation for the edits. \jessie{danke}}

@@

\section{Omitted Proofs}\label{app:omitted-proofs}
\begin{proposition}\label{prop:elic-cplx-lb-ccdim}
	Consider the discrete loss $\ell : \R \times \Y \to \reals_+$ and $\gamma:= \prop{\ell}$.
	Then $\eliccvx(\gamma) \leq \ccdim(\ell)$.
\end{proposition}
\begin{proof}
	Let $d$ be the convex calibration dimension of $\ell$, and $(L, \psi)$ be calibrated with respect to $\ell$ with $L$ convex.
	Then $L$ indirectly elicits $\gamma$ by Lemma~\ref{lem:calib-implies-indir}.
\end{proof}
\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
	%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
	Now consider $v \in F - p$.
	Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
	%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
	%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
	%  
	%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
	%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
	%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}

The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\simplex}$.
\newcommand{\simplexp}{\Delta_{\Y'}}
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \simplex \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

\hariresult*
\begin{proof}
	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$, and consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
	Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.

	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
	%	First, for intuition, consider $p \in \relint{\simplex}$. 
	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
	%
	%	
	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
	%	
	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	%	\begin{align*}
	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	%	\end{align*}
	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
	%
	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
